Ages of Young Stars and Planets in the Kepler Field

### 2024-06-17 paper/ms.tex
update ms (add mcquillan only appendix)

>>>>

\section{What if we only considered McQuillan's periods?}

We argued in Section~\ref{subsec:rotsel} that our choice of adopting
the periods from \citet{Santos_2019,Santos_2021} yielded
the best possible balance between homogeneity and sensitivity for 
both Kepler targets and for KOIs.
Nonetheless, it is interesting to consider whether our
analysis of the Kepler field's rotation-based age distribution is robust to
this choice, for instance compared to adopting only the rotation periods from
\citet{McQuillan_2014}.  
Figures~\ref{fig:prot_vs_teff_mcq} and~\ref{fig:hist_tgyro_mcq}
repeat the analysis, but make this alternate choice.
Figure~\ref{fig:prot_vs_teff_mcq} shows that while the overall contours
of the $P_{\rm rot}$ vs.~$T_{\rm eff}$ distribution are similar between
the two samples, the \citeauthor{Santos_2019} distribution includes more stars,
particularly at longer rotation periods.
The impact of this on the inferred rotation-based age distributions
(Figure~\ref{fig:hist_tgyro_mcq}) is that while the
\citeauthor{Santos_2019} distribution peaks at 2.8-3.0\,Gyr,
the \citeauthor{McQuillan_2014} distribution peaks at 2.4-2.6\,Gyr.
A number of metrics shift.
For instance, the ratio of the star formation rate 3\,Gyr age to today
is \ratiosfr$\pm$\uncratiosfr\ assuming the \citeauthor{Santos_2019} periods,
and \mcquillanonlyratiosfr$\pm$\mcquillanonlyuncratiosfr\ assuming
the \citeauthor{McQuillan_2014} periods.
Similarly, the ratio of ``old'' (2-3\,Gyr) to ``young'' (0-1\,Gyr) stars
shifts from \ratioobtoybstars\ in the \citeauthor{Santos_2019} case
to \mcquillanonlyratioobtoybstars\ in the \citeauthor{McQuillan_2014}
case.
The K dwarf age distributions (Figure~\ref{fig:hist_tgyro_mcq}) however appear 
quite similar.
Generally, we believe these plots support the conclusion that the $t_{\rm gyro}$
age distribution in the Kepler field is highly non-uniform, and likely peaks in the 2.5-3\,Gyr range.

\begin{figure*}[!t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{prot_teff_Santos19_Santos21_dquality.pdf}
		}
		\subfloat{
			\includegraphics[width=0.43\textwidth]{prot_teff_McQuillan2014only_dquality.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Variant of Figure~\ref{fig:prot_vs_teff}}, comparing the default
    rotation periods ({\it left}) from \citet{Santos_2019,Santos_2021}
    against the \citet{McQuillan_2014} rotation periods ({\it right}).
    All stars are required to be amenable to rotation-based age dating
    (i.e.~none of bit flags zero through nine raised).
	}
	\label{fig:prot_vs_teff_mcq}
\end{figure*}

\begin{figure*}[!th]
  \begin{center}
    \leavevmode
    \subfloat{
        \includegraphics[width=.85\textwidth]{mcq_santos_comp_top.pdf}
    }

	\vspace{-0.35cm}
    \subfloat{
        \includegraphics[width=.85\textwidth]{mcq_santos_comp_bottom.pdf}
    }
  \end{center}
  \vspace{-0.66cm}
  \caption{{\bf Variant of Figure~\ref{fig:hist_tgyro},} comparing
  our default adopted catalog of \citet{Santos_2019,Santos_2021}
  rotation periods against the rotation periods
  reported by \citet{McQuillan_2014}.
  \label{fig:hist_tgyro_mcq}
  }
\end{figure*}
